---
title: "Assignment 2 MATH 208  (Question 2)"
output:
  pdf_document: default
  html_document: default
---
Parsa Yadollahi \newline
260869949 \newline
MATH 208 - Assignment 2\newline
```{r include=FALSE}
library(tidyverse)
library(ggplot2)
library(heplots)
library("dplyr")
```


## Question 2
a) 
```{r}
data(Diabetes)
df_diabetes = as_tibble(Diabetes)
df_grouped = df_diabetes %>% 
  group_by(group) %>% 
  summarise_all(list(
    Avg=mean,
    Med=median
    )
  ) %>% 
  pivot_longer(
    col=contains('_'),
    names_to = "Measure") %>% 
pivot_wider(
  id_cols = Measure, 
  names_from = group
  ) %>%  
  arrange(
    desc(Measure)
    )

df_grouped
```
The variable that seem to differentiate amongst the different types of diabetes is glutest, intest, glufast and sspg


b)
```{r}
df_test = df_diabetes %>% group_by(group)
ggplot(df_diabetes, aes(x=glutest, y=instest, col = group)) + geom_point() +
  labs(title="Glucose vs. Insulin Test", x="Gluetest", y="Intest")

ggplot(df_diabetes, aes(x=glutest, y = sspg, col = group)) + geom_point() +
  labs(title="Glucose vs. SSPG Test", x="Gluetest", y="SSPH")

ggplot(df_diabetes, aes(x=instest, y = sspg, col = group)) + geom_point() +
  labs(title="Insulin vs. SSPG Test", x="Gluetest", y="SSPG")

```

Glucose vs. SSPG test seem to return the greatest distinction looking at the plots above

c)
```{r}
# Group data
group_normal = df_diabetes[df_diabetes$group == "Normal",]
group_chemical = df_diabetes[df_diabetes$group == "Chemical_Diabetic",]
group_overt = df_diabetes[df_diabetes$group == "Overt_Diabetic",]

# Histograms
ggplot(group_normal, aes(x=glutest, y=sspg)) + geom_bin2d(bins=15) +
labs(x="Glucose test", y="SSPG")

ggplot(group_chemical, aes(x=glutest, y=sspg)) + geom_bin2d(bins=15) +
labs(x="Glucose test", y="SSPG")

ggplot(group_overt, aes(x=glutest, y=sspg)) + geom_bin2d(bins=15) +
labs(x="Glucose test", y="SSPG")


# contour plot
ggplot(group_normal, aes(x=glutest,y=sspg)) + geom_density_2d(col="red") +
  labs(x="Glucose test", y="sspg") + xlim(c(200,500)) + ylim(c(-50,350))

ggplot(group_chemical, aes(x=glutest,y=sspg)) + geom_density_2d(col="red") +
  labs(x="Glucose test", y="sspg") + xlim(c(350,650)) + ylim(c(0,350))

ggplot(group_overt, aes(x=glutest,y=sspg)) + geom_density_2d(col="red") +
  labs(x="Glucose test", y="sspg") + xlim(c(250,2000)) + ylim(c(0,600))

```

Yes, I find the plots provide useful summaries of the differences in the distributions.




















