---
title: "Assignment 2 MATH 208  (Question 1)"
output:
  pdf_document: default
  html_document: default
---
Prsa Yadollahi \newline
260869949 \newline
MATH 208 - Assignment 2\newline



```{r include=FALSE}
library(tidyverse)
library(fivethirtyeight)
library(here)
library(knitr)
library(gridExtra)
library(ggmosaic)
library(ggplot2)
library("dplyr")
data(biopics)
```


a)
```{r}
ggplot(data=biopics, aes(x = year_release)) + 
  geom_histogram(aes(),color="black", fill = "white",
                position = "identity", bins = 100)
```
From the plot we can deduct that in general the total number of biopics released per year has increased over time based on the timeline above.
b)
```{r}
ggplot(data=biopics, aes(x = year_release, group=subject_sex, fill = subject_sex)) + 
  geom_bar(bins = 100, col="black")+ylab("Biopics")+xlab("Year")

```

c)
```{r}
biopics_by_race <- biopics %>% 
  mutate(race=case_when(
      subject_race=="White" ~ "White",
      race_known=="Known"~ "Color",
      TRUE ~ "Unknown"
       )
    )
biopics_by_race[,"race"]

ggplot(biopics_by_race,aes(x=year_release,group=race,fill=race)) + 
  geom_histogram(bins=100,col="black")+ylab("Biopics")+xlab("Year")

```


d)

```{r}
 ggplot(data = biopics_by_race) +
  geom_mosaic(aes(x=product(year_release), fill=interaction(subject_sex, race), na.rm=TRUE)) +
  labs(title='Mosaic plot: Sex vs. Race', x="Year")
```
Based on the graph above. Females who are people of color are the most underrepresented

e)
```{r}
new_biopic = 
  as_tibble(biopics) %>% 
  group_by(year_release) %>% 
  mutate(count=n()) %>% 
  mutate(
  subject_race = 
    ifelse(
      is.na(subject_race),"Unknown",
    ifelse(
      subject_race=="White",subject_race,"Colour"
      )
    )
  ) %>%
  select(
    year_release,
    subject_race,
    subject_sex,
    count
    ) 

new_biopic_summary = new_biopic %>% 
  group_by(
    year_release,
    subject_sex,
    subject_race
  ) %>% 
  mutate(
    number = n(),
    proportion=number/count
    ) 

new_biopic_summary = new_biopic_summary[
  order(
    new_biopic_summary$year_release
    ),
  ] %>% 
  unique(.) %>% 
  select(
    year_release, 
    subject_sex,
    subject_race,
    number,
    proportion
  )
new_biopic_summary 

```


f) i)
```{r}
ggplot(
  data = new_biopic_summary, 
  aes(
    x=year_release,
    y=number,
    fill=interaction(
      subject_sex, 
      subject_race
      )
    )
  ) + 
  geom_point(
    aes(
      color=interaction(
        subject_sex,
        subject_race
        )
      )
    ) +
  geom_line(
    aes(
      color=interaction(
        subject_sex,
        subject_race
        )
      )
    ) +
  labs(title="Summary of gender per race", x = "Year release", y = "Count")
```

ii)
``` {r}
ggplot(
  data = new_biopic_summary, 
  aes(
    x=year_release, 
    y=proportion, 
    fill=interaction(
      subject_sex
      )
    )
  ) + 
  geom_point(
    aes(
      color=interaction(
        subject_sex
        )
      )
    ) +
  geom_line(
    aes(
      color=interaction(
        subject_sex
        )
      )
    ) + 
  labs(title="Relative proportions of subjects over time", x = "Year release", y = "Count") +
  facet_wrap(~intersection(subject_race))
```

From the plots drawn above, we can conclude that the problem of imbalance is getting better.
We note that they are all converging.







